Race results from the twelfth edition of the

### 2025-04-27 inst/volvo.Rmd
soft link for hyper2.bib
ordertable() now deprecated

---
title: "Race results from the twelfth edition of the
  round-the-world Volvo Ocean Race"
author: "Robin K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

```{r readvolvotable}
volvo_table <- ordertable(read.table("volvo.txt"))
volvo_table
```

Thus the first column refers to leg 1, in which competitor Abu Dhabi
came first, Brunel third, and so on.  Here, `DNF` signifies "did not
finish" and `DNS` "did not start".  We can convert the table to a
support function with `ordertable2supp()`, remembering to specify the
noscore options:

>>>>

---
title: "Race results from the twelfth edition of the
  round-the-world Volvo Ocean Race"
author: "Robin K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

```{r readvolvotable}
volvo_table <- read.table("volvo.txt")
volvo_table
```

Thus the first column refers to leg 1, in which competitor Abu Dhabi
came first, Brunel third, and so on.  Here, `DNF` signifies "did not
finish" and `DNS` "did not start".  We can convert the table to a
support function with `suppfun()`, remembering to specify the
noscore options:
